Publicity Outreach for ``Quantum interval-valued probability: Contextuality and the Born rule''

### 2018-04-17 revised_prop_letter_publicity.tex
revised_prop_letter_publicity.lyx Updating...

%% LyX 2.2.3 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[english]{article}
\usepackage[T1,T2A]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{verbatim}

@@

\usepackage{babel}
\begin{document}

@@

\maketitle
Randomness is used in cryptography, randomized algorithms, and gambling
\cite{PironioAcinMassarEtAl2010,MillerShi2016}...\ etc. However,
it is impossible to prove randomness definitely \cite{Kleppe2004,Shi2015,Random2018}.
While some people believe quantumness implies randomness \cite{Colbeck2006,Shi2015,MillerShi2016,Yuan2017},
the quantum theory might even be deterministic if it could be simulated
by a deterministic hidden variable model~\cite{EPR1935}. Although
the Bell \cite{Bell1964,Redhead1987-REDINA,peres1995quantum} and
Kochen-Specker \cite{BELL_1966,kochenspecker1967,Redhead1987-REDINA,peres1995quantum}
theorems respectively exclude any local and non-contextuality hidden
variable model for any Hilbert space of dimension $d\ge3$, Meyer
claimed that finite-precision measurements invalidate the spirit of
the Kochen-Specker theorem~\cite{PhysRevLett.83.3751}. In our investigation~\cite{THOS2017},
we employ an interval-valued framework to establish bounds on the
validity of the Kochen-Specker theorem in realistic experimental environments.
In another word, when measurements are precise enough, quantum-mechanical
contextuality continues to hold, maintaining the Kochen-Specker result,
and our results provide additional trust of the randomness of quantum
theory.

>>>>

%% LyX 2.3.0 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass{article}
\usepackage[T1,T2A]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{verbatim}

@@

\usepackage[french,main=english]{babel}
\begin{document}

@@

\maketitle
Randomness is used in cryptography, randomized algorithms, and gambling
\cite{PironioAcinMassarEtAl2010,MillerShi2016}...\ etc. However,
it is impossible to prove randomness definitely \cite{Kleppe2004,Shi2015,Random2018}.
While some people believe quantumness implies randomness \cite{Colbeck2006,Shi2015,MillerShi2016,Yuan2017},
the quantum theory might even be deterministic if it could be simulated
by a deterministic hidden variable model~\cite{EPR1935}. Although
the Kochen-Specker \cite{BELL_1966,kochenspecker1967,Redhead1987-REDINA,peres1995quantum}
theorem exclude any non-contextuality hidden variable model for any
Hilbert space of dimension $d\ge3$, Meyer claimed that finite-precision
measurements invalidate the spirit of the Kochen-Specker theorem~\cite{PhysRevLett.83.3751}.
This claim was countered in the same year by Havlicek et al.~\cite{HKSS1999}
and Mermin~\cite{Mermin1999} and the debate continues to be an active
topic of research \cite{Kent1999,SimonBruknerZeilinger2001,Cabello2002,Appleby2002,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
In our investigation~\cite{THOS2017}, we employ an interval-valued
framework to establish bounds on the validity of the Kochen-Specker
theorem in realistic experimental environments. In another word, when
measurements are precise enough, quantum-mechanical contextuality
continues to hold, the Kochen-Specker theorem maintains, and our results
provide additional trust of the randomness of quantum theory.
